% ************************** Thesis Acknowledgements **************************

\begin{acknowledgements}

I would like to thank my mother and my brother for their unconditional love, support and understanding through these past three years at USP. Their encouragement has given me the motivation to keep going. They were with me every step of the way -- even though physically apart.

\bigskip
I would like to express deepest my gratitude to my adviser Prof. Sandra Aluisio, for the continuous support, patience and never-ending enthusiasm. Not only her guidance helped to develop my research, but also provided the moral support that I needed to move in the roughroad of writing a thesis. Thanks for being so open-minded in your research and willing to take risks. I admire your courage of advising a linguist in a complete new area of study.

\bigskip
My sincere thanks also goes to Prof. Tha\"is Crist\'ofaro for being such a passionate, wholehearted and inspiring scientist. Thanks to her I was introduced to the world of Phonology -- and I fell in love with it. Thanks for enlightening me the first glance of research.

\bigskip
I am also very grateful for all my fellow labmates at NILC. My time in S\~ao Carlos would not have been the same without them: Andr\'e Cunha, Erick Fonseca, Fernando Asevedo, Pedro Balage, Lucas Avan\c{c}o, Nathan Hartmann, Alessandro Bokan, Marco Sobrevilla and Roque Lopez. Juliana Balage and Fernanda Bontempo should also be included in this list, although not being labmates.

\bigskip
Linguists deserve a separate paragraph. D\'ebora Garcia and Amanda Rassi, thanks for the wonderful time and the lovely discussions.

\bigskip
Thanks Christopher Shulby and Vanessa Marquiaf\'avel for their friendship, for being an amazing team and for having the boldness to face the unknown. Mari Shulby and Thor Shulby should also be included here.

\bigskip
Also, I would like to thank all my friends and colleagues from the Phonology Lab: Marco Fonseca, Ricardo Napoleão, Maria Cantoni, Jamila Rodrigues, Iiris Renicke, Bianka Andrade, Leo Almeida, Janaína Rabelo, Ingrid Castro and Fred Baumgratz. A special thanks to Victor Medina, who also helped me with the review.

\bigskip
Several professors have contributed to my journey through Speech Sciences, my gratitude goes to Prof. Sara Candeias, Prof. Aldebaro Klautau, Prof. Fernando Perdig\~ao, Prof. Heliana Mello, Prof. Tommaso Raso, Prof. Thiago Pardo, Prof. Gra\c{c}a Nunes, Prof. M\'arcia Can\c{c}ado, Prof. Solange Rezende and Prof. Gra\c{c}a Pimentel.

\bigskip
My gratitude also goes to CNPq and to Samsung Eletr\^onica da Amaz\^onia Ltda. for funding part of my research.

\bigskip
Finally, I would like to thank Re\~ao Toniazzo for being the most amazing partner, friend and lover I could ever dream of. His everlasting patience and \emph{malemolente} love kept me sane during hundreds of hours of work. Thanks for always being there to listen and to let me get my anxities out, especially when I was too grumpy. You make me a better person. 

\vfill
Gustavo Augusto de Mendon\c{c}a Almeida
\end{acknowledgements}
