%************************************************
\chapter{Introduction}\label{ch:introduction}
%************************************************

\section*{Setting and Motivation}

According to the International Monetary Found (IMF) \cite{IMF2015}, Brazil was the seventh largest economy in the world in 2015 with a GDP of US\$ 2.34 trillions. A survey by The Economist (2013) states that, since 2009, the growth of BRICS accounts for 55\% of the entire world economy growth. The current economic scenario is extremely favourable for Brazil to increase its global influence; however, with regard to the ability to communicate globally, Brazil occupies a much more modest position. 

In 2015, Brazil ranked 41\textsuperscript{st} out of 70 countries in the \ac{EF-EPI} \cite{EF2015}, being classified among countries with low English proficiency, with 51.05 points. Scandinavian countries led the very high proficiency ranking, with Sweden (70.94) in the first position, Denmark (70.05) in third place and Norway (67.83) in fourth. Brazil's performance was close to several other Latin American countries, such as Peru (52.46), Chile (51.88), Ecuador (51.67), Uruguay (50.25) and Colombia (46.54). The only exception in Latin America was Argentina, which, despite the country's turbulent economic situation, was ranked 15\textsuperscript{th}, being classified as high proficiency, with a score of 60.26.

The \ac{EF-EPI} bands are aligned with the \ac{CEFR}, which is a guideline proposed by the Council of Europe to describe achievements of learners of foreign languages across the European Union. The \ac{CEFR} reference levels are described in \autoref{tab:cefr-levels}. \ac{EF-EPI} bands are mapped into \ac{CEFR} reference levels as follows: the very high proficiency band corresponds to \ac{CEFR} level B2; very low proficiency to A2; high, moderate and low proficiency bands to B1 with different punctuations. Brazil's low proficiency rank is analogous to the \ac{CEFR} B1 level. 

\begin{table}[!htpb]
\newcolumntype{A}{>{\centering\arraybackslash}m{.12\textwidth}}
\newcolumntype{B}{>{\centering\arraybackslash}m{.12\textwidth}}
\newcolumntype{C}{>{\arraybackslash}m{.64\textwidth}}
\caption{CEFR reference levels.}
\scriptsize
\begin{center}
\begin{tabular}{ABC}
\hline
\textbf{ Group} & \textbf{Level} & \textbf{\centering Description} \\ \hline
\multicolumn{ 1}{A}{\textbf{Basic User
(A)}} & \multicolumn{ 1}{B}{\textbf{Beginner (A1)}} & Can understand and use familiar everyday expressions and very basic phrases aimed at the satisfaction of needs of a concrete type. \\ 
\multicolumn{ 1}{A}{} & \multicolumn{ 1}{B}{} & Can introduce him/herself and others and can ask and answer questions about personal details such as where he/she lives, people he/she knows and things he/she has. \\ 
\multicolumn{ 1}{A}{} & \multicolumn{ 1}{B}{} & Can interact in a simple way provided the other person talks slowly and clearly and is prepared to help. \\ \cline{ 2- 3}
\multicolumn{ 1}{A}{} & \multicolumn{ 1}{B}{\textbf{Elementary (A2)}} & Can understand sentences and frequently used expressions related to areas of most immediate relevance (e.g. very basic personal and family information, shopping, local geography, employment). \\ 
\multicolumn{ 1}{A}{} & \multicolumn{ 1}{B}{} & Can communicate in simple and routine tasks requiring a simple and direct exchange of information on familiar and routine matters. \\ 
\multicolumn{ 1}{A}{} & \multicolumn{ 1}{B}{} & Can describe in simple terms aspects of his/her background, immediate environment and matters in areas of immediate need. \\ \hline
\multicolumn{ 1}{A}{\textbf{Independent User 
(B)}} & \multicolumn{1}{B}{\textbf{Intermediate (B1)}} & Can understand the main points of clear standard input on familiar matters regularly encountered in work, school, leisure, etc. \\ 
\multicolumn{ 1}{A}{} & \multicolumn{ 1}{B}{} & Can deal with most situations likely to arise while traveling in an area where the language is spoken. \\ 
\multicolumn{ 1}{A}{} & \multicolumn{ 1}{B}{} & Can produce simple connected text on topics that are familiar or of personal interest. \\
\multicolumn{ 1}{A}{} & \multicolumn{ 1}{B}{} & Can describe experiences and events, dreams, hopes and ambitions and briefly give reasons and explanations for opinions and plans. \\ \cline{ 2- 3}
\multicolumn{ 1}{A}{} & \multicolumn{ 1}{B}{\textbf{Upper intermediate (B2)}} & Can understand the main ideas of complex text on both concrete and abstract topics, including technical discussions in his/her field of specialization. \\ 
\multicolumn{ 1}{A}{} & \multicolumn{ 1}{B}{} & Can interact with a degree of fluency and spontaneity that makes regular interaction with native speakers quite possible without strain for either party. \\ 
\multicolumn{ 1}{A}{} & \multicolumn{ 1}{B}{} & Can produce clear, detailed text on a wide range of subjects and explain a viewpoint on a topical issue giving the advantages and disadvantages of various options. \\ \hline
\multicolumn{ 1}{A}{\textbf{Proficient User
(C)}} & \multicolumn{ 1}{B}{\textbf{Advanced (C1)}} & Can understand a wide range of demanding, longer texts, and recognize implicit meaning. \\ 
\multicolumn{ 1}{A}{} & \multicolumn{ 1}{B}{} & Can express ideas fluently and spontaneously without much obvious searching for express \\ 
\multicolumn{ 1}{A}{} & \multicolumn{ 1}{B}{} & Can use language flexibly and effectively for social, academic and professional purposes. \\ 
\multicolumn{ 1}{A}{} & \multicolumn{ 1}{B}{} & Can produce clear, well-structured, detailed text on complex subjects, showing controlled use of organizational patterns, connectors and cohesive devices. \\ \cline{ 2- 3}
\multicolumn{ 1}{A}{} & \multicolumn{ 1}{B}{\textbf{Proficiency (C2)}} & Can understand with ease virtually everything heard or read. \\ 
\multicolumn{ 1}{A}{} & \multicolumn{ 1}{B}{} & Can summarize information from different spoken and written sources, reconstructing arguments and accounts in a coherent presentation. \\ 
\multicolumn{ 1}{B}{} & \multicolumn{ 1}{B}{} & Can express him/herself spontaneously, very fluently and precisely, differentiating finer shades of meaning even in the most complex situations. \\ \hline
\end{tabular}
\end{center}
\label{tab:cefr-levels}
\end{table}

As one might notice, the B1 level describes an individual who is usually able to understand familiar matters, deal with travelling situations, describe personal experiences and plans, and produce simple texts about subjects of personal interest. Needless to say, this is a very restricted communicative competence, which limits English usage primarily to the personal domain. 

With respect to Business English proficiency, Brazil's performance is even more concerning. In the 
Business English Index (BEI) of 2013 \cite{BEI2013}, Brazil reached the 71\textsuperscript{st} position out of 77 countries analysed. The country attained a score of 3.27 points, in a scale from 1 to 10, being placed at the ``Beginner'' range, the lowest range considered by the index. Brazil was close to countries such as El Salvador (3.24), Saudi Arabia (3.14) and Honduras (2.92), which up until recently had experienced civil wars or dictatorship governments. BEI describes individuals at the beginner level as those who ``can read and communicate using only simple questions and statements, but can't communicate and understand basic business information during phone calls''. Again, we can see that this is a very limited linguistic competence, that would not allow one not even to perform the most elementary day-to-day task in a company or industry work environment. 

Given this scenario, it is clear that we  need to improve English language proficiency among Brazilians. 
\ac{CALL} systems can be of great help in this scenario. These systems have several benefits, such as \cite{Witt1999}: 

\begin{itemize}
 \item Providing undivided attention to the user, as opposed to a classrom environment, where teachers need to share attention among all students.
 \item Being cheap and scaling well as what all students need is access to a computer.
 \item Enabling asynchronous learning, allowing people with time and place constraints to study at their own pace and schedule.
 \item High degree of individuality regarding the choice of material which is studied.
\end{itemize}

Obviously, there are disadvantages too. The limited interaction and feedback is often mentioned as a major problem in \ac{CALL}. Nevertheless, some studies have shown that students who used \ac{CALL} for training pronunciation training achieved equivalent results to students who were enrolled in traditional classes, with teacher-led pronunciation training \cite{Neri2008, Stenson2013}.

\section*{Gap and objectives} 

This project seeks to be a primary step towards developing a \ac{CAPT} for Brazilian-accented English. The initial plan was to focus on methods for creating \ac{CAPT} systems for Brazilian-accented English by embedding as much phonetic knowledge as possible. As Witt \citep{Witt2012} points out in her survey on \ac{CAPT} from 2012, back then, one of the core challenges in the area was that \ac{ASR} systems were not able to provide a reliable signal in terms of phone recognition. Our hypothesis was that by integrating phonetic knowledge in all stages of the pipeline for a \ac{CAPT}, one would be able to improve the accuracy of the system and provide more trustworthy results.

However, as the project went through, with a broader view of the literature in \ac{CAPT} and a more profound understading of how \ac{ASR} works, such plan has shown to be unfeasible in the time given for a Master's Course. Due to the scarcity of resources, it was not possible to replicate for Brazilian-accented English several of the existing methods that were applied to other languages in the literature. For Brazilian-accented English, the only speech corpus currently available is the Corpus Oral de Brasileiros Aprendizes de Ingl\^es (COBAI) \cite{Mello2012}, which is not suitable for speech recognition, due to the fact that the files are too long, usually consisting of interviews with 5 minutes; for training acoustic models, sentences should have around 10 seconds in order to get correct phone alignments. There were no specialized corpora for speech recognition in Brazilian-accented English, no language models trained from learners' texts and no dictionaries with pronunciation variants. 

Instead, we decided to focus on investigating and building resources for Natural Language Processing and Pronunciation Evaluation which, in the future, may somehow help the development of \ac{CAPT} systems for Brazilian-accented English. We worked particularly with tools and resources for text-to-speech, spelling correction, corpus building and automatic pronunciation assessment. In all cases, we attempted to integrate and embed phonetic knowledge in the pipeline.

\section*{Research Hypothesis}

\paragraph*{Text-to-speech}
  \begin{enumerate}
    \item A hybrid approach, which includes both manual rules and machine learning, can be used to achieve state-of-the-art results for \ac{G2P} conversion in Brazilian Portuguese.
    \item Supra-segmental information, such as lexical stress and syllable boundary, are useful for improving the accuracy of a \ac{G2P} for \ac{BP}, especially with regard to vowel transcription.
    \item Part-of-speech tags are able to provide enough information for a hybrid \ac{G2P} to distinguish between heterophonic homograph pairs, such as "gov[\textipa{e}]rno" (government) "gov[\textipa{E}]rno" (I govern).
  \end{enumerate}

\bigskip
\paragraph*{Spelling correction}
  \begin{enumerate}
    \setcounter{enumi}{4}
    \item A considerable part of the typos that users make are phonologically-motivated, therefore phonetic transcription can be used to improve the coverage of spelling correction systems.
  \end{enumerate}

  
\paragraph*{Corpus building}
  \begin{enumerate}
    \setcounter{enumi}{5}
    \item Greedy algorithms can help to produce richer speech corpora by making local optimal decisions, through analysing the triphone sequences of the sentences in a corpus and extracting those which keep the triphone distribution as uniform as possible in each iteration.
  \end{enumerate}

  
\paragraph*{Automatic pronunciation assessment}
  \begin{enumerate}
    \setcounter{enumi}{6}
    \item Multipronunciation dictionaries with hand-written rules for generating variants are a reliable source of pronunciation information for pronunciation assessment.
    \item Acoustic models trained on phonetically-rich speech corpora are able to provide more accurate phone models than those trained on balanced corpora.
    \item Context-free grammars can be adapted for forced-alignment recognition to list all pronunciation variants of a given word without hindering the performance of the \ac{ASR}.
    \item Combined acoustic models (trained over native corpora + interlanguage data) have phone models which are robust enough to perform speech recognition in all languages used for training.
    \item The additional pronunciation variants do not harm the performance.
  \end{enumerate}

  
\section*{Contributions of the Thesis} 

Within this work, we have investigated and developed a set of tools and resources which integrate phonetic knowledge -- and benefit from it. Some of these tools were created and tested in tasks related to processing Brazilian-accented English or Brazilian Portuguese, but their architecture and methods are certainly scalable to other languages or scenarios. The full list of contributions is provided below\footnote{All files, resources and scripts developed are available at the project website: \emph{(http://nilc.icmc.usp.br/listener)}. Due to copyright reasons, the corpora used for training the acoustic models cannot be made available.}:

\begin{enumerate}
 \item \emph{Aeiouad\^o G2P}: A grapheme-to-phoneme converter for \ac{BP} which uses a hybrid approach, based on both handcrafted rules and machine learning method, as published in \citeauthor{Mendonca2014} \cite{Mendonca2014}. \emph{Aeiouad\^o dictionary}: A large machine readable dictionary for \ac{BP}, compiled from a word list extracted from the Portuguese Wikipedia, which was preprocessed in order to filter loanwords, acronyms, scientific names and other spurious data, and then transcribed with Aeiouad\^o G2P).
 \item A phonetic speller for user-generated content in \ac{BP}, based on machine learning, which takes advantage of Aeiouad\^o G2P to group phonetically related words, as described in \citeauthor{Mendonca2015} \cite{Mendonca2015}; 
 \item A method for the extraction of phonetically-rich sentences, i.e. sentences with a high variety of triphones distributed in a uniform fashion, which employs a greedy algorithm for comparing triphone distributions among sentences, as presented in \citeauthor{Mendonca2014b} \cite{Mendonca2014b};
 \item \emph{Listener}: A prototype system for automatic speech recognition and evaluation of Brazilian-accented English, which makes use of forced alignment, \ac{HMM}/\ac{GMM} acoustic models, context-free grammars and multipronunciation dictionaries, as presented in \citeauthor{Mendonca2016} \cite{Mendonca2016};
\end{enumerate}

\section*{Thesis Structure}

This Master's thesis is organised into four chapters and follows the structure of a sandwich thesis, consisting of a collection of published or submitted articles. Chapter ~\ref{ch:foundations} presents the theoretical foundations, with an introduction to phonetics, as well as automatic speech recognition. Chapter ~\ref{ch:articles} contains all articles that were published throughout the execution of this work or which are in-press. Section ~\ref{sec:aeiouado} presents the Aeiouad\^o's dictionary and \ac{G2P} converter, which was built uppon a hybrid strategy for converting graphemes into phones, with manual transcription rules, as well as machine learning. Section ~\ref{sec:speller} presents a use case of Aeiouad\^o, namely a phonetic-speller which employs the transcriptions generated by the grapheme-to-phoneme converter. Section ~\ref{sec:phon-rich} proposes a method for the extraction of phonetically-rich sentences, which can be used for building more representative speech corpora. Section ~\ref{sec:listener} describes a prototype system for non-native speech recognition and evaluation of Brazilian-accented English, which makes use of the tools and resources developed in this thesis. Finally in Chapter ~\ref{ch:conclusions}, we present the overall conclusions, some limitations we found, together with the next steps for future work.